% !TEX program = xelatex

\documentclass{chicv}

% optionally suppress printing the page number
\pagenumbering{gobble}

\begin{document}

%% basic personal info
\name{ChengXiang Qi}
\begin{basicinfo}
  \info{\email{18630816527@163.com}}
  \info{\homepage{kuangjux.top}[https://kuangjux.top]}
  \info{\github{KuangjuX (\textbf{185} followers)}[https://github.com/KuangjuX]}
  \info{\linkedinsquare{KuangjuX}[https://www.linkedin.com/in/kuangjux/]}
  % \phone{}
\end{basicinfo}

\section{Education}
\cventry{TianJin University}
  {September 2019 -- June 2023(Expected)}
  [Computer Science and Technology]
  [TianJin, China]



\section{Selected Projects}

\cventry{xv6-rust}
  {03/2021 - 08/2021}
  [MIT xv6-riscv implemented by Rust]
  [\iconlink[\faGithub][Ko-oK/xv6-rust(\faIcon[regular]{star}111)]{https://github.com/Ko-oK-OS/xv6-rust}]
  \begin{itemize}
    \item A Unix-like operating system implemented pure rust. 
    \item Optimize memory module using Buddy Sytem.
    \item Redesign Spinlock/Sleeplock as smart pointer.
    \item Optimize file system, making it support Rust features.
  \end{itemize}

  \cventry{rCore-fat}
  {07/2021 - 08/2021}
  [A operaing system based rCore-tutorial-v3 with fat32 file system]
  [\iconlink[\faGithub][rCore-fat]{https://github.com/KuangjuX/rCore-fat}]
  \begin{itemize}
    \item Design fat32 file system for rCore-Tutorial-v3, it is a alternative topic of rCore OS community in Summer OSPP 2021.
  \end{itemize}

  \cventry{TrivialTCPStack}
  {08/2021 - 09/2021}
  [A TCP/IP stack implemented in pure C]
  [\iconlink[\faGithub][TrivialTCPStack]{https://github.com/KuangjuX/TrivialTCPStack}]
  \begin{itemize}
    \item A TCP/IP stack which use UDP to simulate low level network environment. This project is the final project of Computer Netword Coursera.
    \item Implement three-way handshake, Go-Back-N, sliding window and so on.
    \item Implement a Linux-like timer.
  \end{itemize}

  \cventry{mini-game-os}
  {07/2022 - Now}
  [A bare metal game running in raspberry pi 4 written in Rust]
  [\iconlink[\faGithub][raspberrypi-embedded/mini-game-os]{https://github.com/raspberrypi-embedded/mini-game-os}]
  \begin{itemize}
    \item This is my hobby project and also my first try to explore embedded system in Rust 
    \item It is designed for playing simple games such as snake game, flappy bird and son 
    \item It can run QEMU and raspberry pi 4B.
  \end{itemize}

  \cventry{Other Projects}{}
  \begin{itemize}
    \item \textbf{xv6-riscv-solution}(\faIcon[regular]{star}26):
    {\small My solution and notes for MIT 6.S081 OS Course labs.} [\iconlink[\faGithub][xv6-riscv-solution]{https://github.com/KuangjuX/xv6-riscv-solution}]
    \item \textbf{NEMU-x86}(\faIcon[regular]{star}10):
    {\small NEMU is a simple but complete full-system emulator designed for teaching purpose. I finished it during Computer Organization and System Course.}  [\iconlink[\faGithub][NEMU-x86]{https://github.com/KuangjuX/NEMU-x86}]
    \item \textbf{NSCSCC-2022-TJU/ChiselMIPS}(\faIcon[regular]{star}9):
    {\small ChiselMIPS is a five-stage CPU with instruction cache, data cache and TLB written in Chisel for NSCSCC 2022.} [\iconlink[\faGithub][NSCSCC-2022-TJU/ChiselMIPS]{https://github.com/NSCSCC-2022-TJU/ChiselMIPS}]
    \item \textbf{SimpleMIPS}(\faIcon[regular]{star}5):
    {\small SimpleMIPS is a classical five-stage pipelined CPU written in verilog that supports 57 MIPS instructions. } [\iconlink[\faGithub][SimpleMIPS]{https://github.com/KuangjuX/SimpleMIPS}]
    \item \textbf{SimpleDB}:
    {\small My solution for CMU 15445/645 lab. } [\iconlink[\faGithub][SimpleDB]{https://github.com/KuangjuX/SimpleDB}]
  \end{itemize}
  

\section{Selected Awards}
\begin{itemize}
  \item NSCSCC Team Competition Third Prize in 2022
  \item OSCOMP Team Competition Thrid Prize in 2021
  \item The Best Quality Award in Summer OSPP 2021
\end{itemize}

\section{Experiences}
\cventry{Part-Time Student Research}{03/2022 - 05/2022}
\begin{itemize}
  \item Participate in HuaWei hardware project, design \& implement a huffman compression using verilog based on [\iconlink[\faGithub][zstd compression algorithm]{https://github.com/facebook/zstd}].
\end{itemize}
\cventry{Summer OSPP 2021}
{07/2021 - 10/2021}
\begin{itemize}
  \item I join rcore-os commuinity and design fat32 file system for rCore-Tutorial-v3.
\end{itemize}

\cventry{Teaching Assignment}
{09/2021 - 11/2021}
\begin{itemize}
  \item Pratice of ICS in 2021, I help students complete NEMU(a x86-32 software emulator).
\end{itemize}

\cventry{TWT Studio}
{09/2019 - 01/2021}
\begin{itemize}
  \item Maintain Part Management System 
  \item Develop Intramural Forum System in WeiPeiYang
  \item Develop AT(a office automation system)
\end{itemize}



\section{Skills}

\begin{compactlist}
  \item \textbf{Programming Languages}: Rust, C/C++, Go, Python, HTML/CSS/JavaScript, PHP
  \item \textbf{Tools}: Visual Studio Code, gdb, GNU make, CMake, QEMU, Docker
  \item \textbf{Tech Skills}: OS Kernel, Low level software development, Backend and Frontend
\end{compactlist}

\section{Others}
\begin{itemize}
  \item Self taught CMU 15-445, MIT 6.S081 and other public courses and finish lab assignments 
  \item Interested OS, Distributed System, Embedded System 
  \item Persoanl open source projects have earned more than 200 stars.
\end{itemize}

\end{document}